---
title: 'Geographic Data Visualization: a basic debrief on Chipole restaurants'
author: "Allen Xu"
date: "9/12/2020"
output: html_document
---
*In this report, I will try to perform data visualization of Chipole restaurants' distribution in U.S. using leaflet packages*
<br><br>

## preparation

```{r load packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(usmap)
library(leaflet)
library(maps)
```
<br><br>

## overall look
<br><br>
*First we begin by taking an overlook of chipole distribution by state. We used the location dataset available from Kaggle.*
<br><br>
```{r message=FALSE, warning=FALSE}
location <- read_csv("chipotle_stores.csv")

count <- location %>%
    group_by(state) %>%
    tally()
colnames(count) <- c("full", "count")
```
<br><br>
*In this sections, we used the usmaps package to provide the base picture of U.S. US maps package allows us to change directly on the background element.*
<br><br>
```{r warning=FALSE}
data(statepop)

count <- count %>%
    left_join(statepop, by = "full")
count <- count[,1:4]


plot_usmap(data = count, values = "count") + scale_fill_continuous(low = "white", high = "red", name = "count", label = scales::comma) + theme(legend.position = "right") 
```
<br><br>
*Here we can see usmap package allow us to distinguish between states by another independent variable, in this case it's the count of restaurants*
<br><br>

## specific pins
<br><br>
*The disadvantage of the graph above is that we cannot tell where exactly do the restaurants location within each state. Leaflet helps us to pin specific location on the map*
<br><br>
```{r set up pins}
greenLeafIcon <- makeIcon(
    iconUrl = "http://leafletjs.com/docs/images/leaf-green.png",
    iconWidth = 5, iconHeight = 5,
    iconAnchorX = 5, iconAnchorY = 5,
    shadowUrl = "http://leafletjs.com/docs/images/leaf-shadow.png",
    shadowWidth = 5, shadowHeight = 5,
    shadowAnchorX = 5, shadowAnchorY = 5
)
```
<br><br>
*Here is a display of restaurants in Chicago*
<br><br>
```{r}
leaflet() %>%
    addTiles() %>%  # Add map tiles
    addMarkers(lng=location[location$location == "Chicago",]$longitude, lat = location[location$location == "Chicago",]$latitude, popup = location$address)

```
<br><br>
*Then let's try to elaborate the display to a national level*
<br><br>
```{r message=FALSE, warning=FALSE}
mapStates = map("state", fill = TRUE, plot = FALSE)
leaflet(data = mapStates) %>% addTiles() %>%
    addPolygons(fillColor = topo.colors(10, alpha = NULL), stroke = FALSE)

m = leaflet() %>% addTiles()
df = data.frame(
    lat = location$latitude,
    lng = location$longitude,
    size = 1,
    color = sample(colors(), nrow(location), replace = TRUE)
)
m = leaflet(df) %>% addTiles()
m %>% addCircleMarkers(radius = ~size, color = ~color, fill = FALSE)

```

